Bare minimum: set theory

### 2021-05-14 BareMinima/SetTheory/BareMinimumSetTheory.tex
BM-SetTheory: more work on cardinals and ordinals

@@

@@

\begin{defn}[Common sets]
	 The \textbf{empty set}
	 \marginleft{Common sets: $\emptyset$, $\mathbb{N}$, $\mathbb{Z}$, $\mathbb{Q}$, $\mathbb{R}$, $\mathbb{C}$}
	  $\emptyset$ is the set with no elements.
	 The \textbf{set of natural numbers} $\mathbb{N} = \{ 0, 1, 2, ... \}$. The \textbf{set of positive natural numbers} $\mathbb{N}^+ = \{n \in \mathbb{N} \, | \, n > 0\}$. The \textbf{set of integer numbers} $\mathbb{Z} = \{ ... , -2, -1, 0, +1, +2, ...\}$. The \textbf{set of rational numbers} $\mathbb{Q}$. The \textbf{set of real numbers} $\mathbb{R}$. The \textbf{set of complex numbers} $\mathbb{C}$. A \textbf{universe} $U$ is the set that, within a specific context, contains all entities under study.
\end{defn}

@@

\begin{defn}[Power set]
	Given a set $A$, its \textbf{power set}, \marginleft{Power set: $2^{A}$, $\mathcal{P}(A)$} noted $\mathcal{P}(A)$ or $2^{A}$, is the set of all subsets of $A$. That is, $\mathcal{P}(A) = \{B \, | \, B \subset A \}$.
\end{defn}

@@

	Let $X \subseteq \mathcal{P}(A)$ be a set of subsets of $A$. The operations of union $\bigcup\limits_{Y \in X} Y$ and intersection $\bigcap\limits_{Y \in X} Y$ can be extend to span all elements.
\end{defn}

We give the following informal definition. Given two elements $a$ and $b$, the \textbf{ordered pair} $(a, b)$ specifies two objects in that order. That is $(a, b) \neq (b, a)$ and $(a, a) \neq \{a\}$.

@@

@@

@@

@@

@@

\begin{defn}[Partitions]
	A \textbf{partition} \marginleft{Partitions} of a set $A$ is a collections $P \subset \mathcal{P}(A)$ of disjoint subsets that cover all of $A$. That is:
	\begin{enumerate}
		\item $\bigcup\limits_{X \in P} X = A$
		\item $X \cap Y = \emptyset$ for all $X, Y \in P$ where $X \neq Y$
	\end{enumerate}
\end{defn}

@@

@@

\subsection{Numeric constructions}
\begin{remark}
	The constructions that follow exemplifies the standard way numbers are defines in mathematics and it is useful to gain certain insights. In the Assumptions of Physics, however, we prefer to understand numbers as order-theoretic concept (i.e. the integer numbers can be thought as a linearly ordered set where each element have an immediate successor and an immediate predecessor).
\end{remark}
\begin{defn}
	Let $A$ be a set. We define the \textbf{successor} $A^+ = A \cup \{A\}$. A set $S$ is called a \textbf{successor set} if it contains the empty set (i.e. $\emptyset \in S$ and if contains the successor of every element (i.e. if $X \in S$ then $X^+ \in S$). The set of \textbf{natural numbers} $\mathbb{N}$ is the intersection of all successor sets.
\end{defn}
\begin{remark}
	The natural numbers so constructed are known as von Neumann ordinals. They are as follows:
	\begin{itemize}
		\item $0 = \{ \} = \emptyset$
		\item $1 = \{ 0 \} = \{ \emptyset \}$
		\item $2 = \{0, 1\} = \{ \emptyset, \{ \emptyset\} \}$
		\item $3 = \{0, 1, 2\} = \{ \emptyset, \{ \emptyset\}, \{ \emptyset, \{ \emptyset\} \} \}$
		\item $4 = \{0, 1, 2, 3\} = \{ \emptyset, \{ \emptyset\}, \{ \emptyset, \{ \emptyset\} \}, \{ \emptyset, \{ \emptyset\}, \{ \emptyset, \{ \emptyset\} \} \} \}$
		\item ...
	\end{itemize}
\end{remark}

@@

Syntactic paradoxes two main strategies. Zermelo–Fraenkel (ZFC) only talk about sets and restrict set construction to subsets only. von Neumann–Bernays–Gödel (NBG) talks about classes and defines sets as those classes that can be elements of classes. Set builder notation works on sets, not classes. So, if putting a class in a class creates a contradiction, it's because the class is not a set, but a proper class.

>>>>

\def\ordinals{\textbf{ORD}}
\def\cardinals{\textbf{CRD}}

\def\ordless{\prec}
\def\ordleq{\preceq}
\def\ordeq{\sim}
\def\ordgeq{\succeq}
\def\ordgtr{\succ}

\def\crdless{\sqsubset}
\def\crdleq{\hookrightarrow}
\def\crdeq{\leftrightarrow}
\def\crdgeq{\hookleftarrow}
\def\crdgtr{\sqsupset}

@@

Ordinal: $\ordless \ordleq \ordeq \ordgeq \ordgtr$

Cardinal: $\crdless \crdleq \crdeq \crdgeq \crdgtr$

@@

\begin{defn}[Common sets]
	 The \textbf{empty set}
	 \marginleft{Common sets: $\emptyset$, $\{a\}$, $\mathbb{N}$, $\mathbb{Z}$, $\mathbb{Q}$, $\mathbb{R}$, $\mathbb{C}$}
	  $\emptyset$ is the set with no elements. A \textbf{singleton} is the set of a single value $\{a\}$.
	 The \textbf{set of natural numbers} $\mathbb{N} = \{ 0, 1, 2, ... \}$. The \textbf{set of positive natural numbers} $\mathbb{N}^+ = \{n \in \mathbb{N} \, | \, n > 0\}$. The \textbf{set of integer numbers} $\mathbb{Z} = \{ ... , -2, -1, 0, +1, +2, ...\}$. The \textbf{set of rational numbers} $\mathbb{Q}$. The \textbf{set of real numbers} $\mathbb{R}$. The \textbf{set of complex numbers} $\mathbb{C}$. A \textbf{universe} $U$ is the set that, within a specific context, contains all entities under study.
\end{defn}

@@

\begin{defn}[Power set]
	Given a set $A$, its \textbf{power set}, \marginleft{Power set:\\ $\mathcal{P}(A)$, $2^{A}$} noted $\mathcal{P}(A)$ or $2^{A}$, is the set of all subsets of $A$. That is, $\mathcal{P}(A) = \{B \, | \, B \subset A \}$.
\end{defn}

@@

	Let $\mathcal{A} \subseteq \mathcal{P}(A)$ be a set of subsets of $A$. The operations of union $\bigcup\limits_{A \in \mathcal{A}} A$ and intersection $\bigcap\limits_{A \in \mathcal{A}} A$ can be extend to span all elements.
\end{defn}

\begin{defn}[Ordered pair]
	Given two \marginleft{Ordered pair: $(a, b)$} elements $a$ and $b$, the \textbf{ordered pair} $(a, b)$ specifies two objects in that order. That is $(a, b) \neq (b, a)$. This can be constructed setting $(a, b) = \{ \{a\}, \{a, b\}\}$.
\end{defn}

@@

\begin{defn}[Disjoint union]
	Let $A$ and $B$ be two sets. The disjoint union $A \sqcup B$ is the union where the elements of the sets are always treated as distinct. That is, $A \sqcup B = \{A\} \times A \cup \{B\} \times B$.
\end{defn}

@@

\begin{defn}
	Let $f : A \to B$ be a function. This induces a relation $f : \mathcal{P}(A) \to \mathcal{P}(B)$ that associates each subset of $A$ to its image and a relation $f^{-1} : \mathcal{P}(B) \to \mathcal{P}(A)$ that associates each subset of $B$ with its reverse image.
\end{defn}

\begin{defn}[Level set]
	A level set \marginleft{Level set} of a function $f : A \to B$ is a set of where the function takes a given value $b$. In other words the reverse image $f^{-1}(\{c\})$ a singleton.
\end{defn}

\begin{prop}
	The induces relations $f : \mathcal{P}(A) \to \mathcal{P}(B)$ and $f^{-1} : \mathcal{P}(B) \to \mathcal{P}(A)$ are functions and satisfy the following properties:
	\begin{enumerate}
		\item $f(\bigcup\limits_{A \in \mathcal{A}} A) = \bigcup\limits_{A \in \mathcal{A}} f(A)$
		\item $f^{-1}(\bigcup\limits_{A \in \mathcal{A}} A) = \bigcup\limits_{A \in \mathcal{A}} f^{-1}(A)$
		\item $f^{-1}(\bigcap\limits_{A \in \mathcal{A}} A) = \bigcap\limits_{A \in \mathcal{A}} f^{-1}(A)$
	\end{enumerate}
\end{prop}

\begin{remark}
	With abuse of notation, $f$ and$f^{-1}$ indicate both the function between elements and sets. The image of the intersection is not in general the intersection of the image. Note how in both topology and measure theory continuity and measurability are defined based on the reverse images.
\end{remark}

@@

\begin{defn}[Restriction]
	Let $f : A  \to B$ \marginleft{Restriction: $f|_C$} be a function and let $C \subseteq B$. Then the \textbf{restriction of $f$ over $C$} is the function $f|_C : C \to B$ such that $f|_C(c) = f(c)$.
\end{defn}

@@

\begin{prop}
	Let $2 = \{0, 1\}$ denote a set with two elements. Then $\mathcal{P}(A)$ and $2^A$ are in one-to-one correspondence.
\end{prop}

@@

\begin{defn}[Partitions]
	A \textbf{partition} \marginleft{Partitions} of a set $A$ is a collections $P \subset \mathcal{P}(A)$ of disjoint subsets that cover all of $A$. That is:
	\begin{enumerate}
		\item $\bigcup\limits_{B \in P} B = A$
		\item $B \cap C = \emptyset$ for all $B, C \in P$ where $B \neq C$
	\end{enumerate}
\end{defn}

@@

\begin{defn}
	Given a function $f : A \to B$ the \textbf{equivalence relation determined by $f$} is the relation $R_f = \{ (a_1, a_2) \, | \, f(a_1) = f(a_2) \}$.
\end{defn}

\begin{prop}[Function canonical decomposition]
	Every function $f : A \to B$ can be written as the composition $f = t \circ s \circ r$ of the following three functions:
	\begin{description}
		\item[$r : A \to A_{/R_f}$] defined as $a \mapsto [a]_{R_f}$; this function is surjective
		\item[$s : A_{/R_f} \to f(A)$] defined as $[a]_{R_f} \mapsto f(a)$; this function is bijective
		\item[$t : f(A) \to B$] defined as $t(b) = b$; this function is injective.
	\end{description}
\end{prop}

@@

\subsection{Numeric constructions}
\begin{remark}
	The constructions that follow exemplifies the standard way numbers are defines in mathematics and it is useful to gain certain insights. In the Assumptions of Physics, however, we prefer to understand numbers as order-theoretic concept (i.e. the integer numbers can be thought as a linearly ordered set where each element have an immediate successor and an immediate predecessor).
\end{remark}
\begin{defn}\label{defn_successor_set}
	Let $A$ be a set. We define the \textbf{successor} $A^+ = A \cup \{A\}$. A set $S$ is called a \textbf{successor set} if it contains the empty set (i.e. $\emptyset \in S$ and if contains the successor of every element (i.e. if $X \in S$ then $X^+ \in S$). The set of \textbf{natural numbers} $\mathbb{N}$ is the intersection of all successor sets.
\end{defn}
\begin{remark}
	The natural numbers so constructed are known as von Neumann ordinals. They are as follows:
	\begin{itemize}
		\item $0 = \{ \} = \emptyset$
		\item $1 = \{ 0 \} = \{ \emptyset \}$
		\item $2 = \{0, 1\} = \{ \emptyset, \{ \emptyset\} \}$
		\item $3 = \{0, 1, 2\} = \{ \emptyset, \{ \emptyset\}, \{ \emptyset, \{ \emptyset\} \} \}$
		\item $4 = \{0, 1, 2, 3\} = \{ \emptyset, \{ \emptyset\}, \{ \emptyset, \{ \emptyset\} \}, \{ \emptyset, \{ \emptyset\}, \{ \emptyset, \{ \emptyset\} \} \} \}$
		\item ...
	\end{itemize}
	It can be shown that they obey Peano's axioms, another common way to axiomatize the natural numbers and their arithmetic.
\end{remark}

\subsection{Ordinal numbers}

For infinite sets, cardinals and ordinals are different since sets of the same infinite size can be given different orderings.

\begin{remark}
	Cardinal numbers (i.e. one, two, three, ...) identify the number of elements in a set. Ordinal numbers (i.e. first, second, third) identify a position within a sequence. Well-ordered sets extend the notion of sequence to arbitrary levels of infinity.
\end{remark}

\begin{defn}[POS]
	A \textbf{partially ordered set}, \marginleft{POS: $(A, \leq_A)$} or \textbf{POS}, is a tuple $(A, \leq_A)$ where $A$ is a set and $\leq_A$ is a partial order over $A$. A \textbf{linearly ordered set} is a POS whose order is linear.
\end{defn}

\begin{defn}[Initial segment]
	The \textbf{initial segment} \marginleft{Initial segment} of a POS $(A, \leq_A)$ determined by $a \in A$ is the set of all elements less than $a$. That is, $S_a=\{ x \in A \, | \, x < a \}$.
\end{defn}

\begin{defn}[Order morphisms]
	Let $(A, \leq_A)$ \marginleft{Order homo/ \\ isomorphism} and $(B, \leq_B)$ be two POSs. An \textbf{order homomorphism} is a function $f : A \to B$ that preserves the ordering. That is, $a_1 \leq_A a_2$ implies $f(a_1) \leq_B f(a_2)$. An \textbf{order isomorphism} is a bijective order homomorphism whose inverse is also an order homomorphism. That is, $b_1 \leq_B b_2$ implies $f^{-1}(b_1) \leq_A f^{-1}(b_2)$.
\end{defn}

\begin{defn}[Well-order]
	A \textbf{well-ordered} \marginleft{Well-order} set is a linearly ordered set $(A, \leq_A)$ where each subset has a least element. That is, for every $B \subseteq A$, there exists an $a \in B$ such that $a \leq_A b$ for all $b \in B$. Let $A$ and $B$ be two well ordered set, we say $A$ \textbf{has lower ordinality than} $B$, noted $A \ordleq B$, if $A$ is order isomorphic to an initial segment of $B$. They have \textbf{the same ordinality}, noted $A \ordeq B$, if they are order isomorphic.
\end{defn}

\begin{prop}[Ordinality]
	If $A$ and $B$ are two well ordered sets, then either $A \ordleq B$ or $B \ordleq A$. If $\mathcal{A}$ is a collection of well-ordered sets, then one element has least ordinality.
\end{prop}

\begin{remark}
	Examples of well-ordered sets:
	\begin{itemize}
		\item a finite sequence: $(a_1, a_2, ..., a_n)$
		\item an infinite sequence: $(a_1, a_2, ..., a_n, ...)$
		\item an infinite sequence with elements afterwards: $(a_1, a_2, ..., a_n, ..., b_1, b_2, ... , b_6)$
	\end{itemize}
	In a well-ordered set, every element always has an immediate successor, but not necessarily an infinite predecessor (e.g. $b_1$ in the third example). 
\end{remark}

\begin{remark}
	Ordinal numbers generalize the construction of von Neumann ordinals and cover all possible positions in well-ordered sets.
\end{remark}

\begin{defn}[Ordinals]
	An \textbf{ordinal} \marginleft{Ordinals: \ordinals} is a set $A$ with the following properties for all $a, b, c \in A$:
	\begin{enumerate}
		\item $a \notin a$
		\item $a \in b$ implies $b \notin a$
		\item $a \in b$ and $b \in c$ implies $a \in c$
		\item $x \in a$ implies $x \in A$
	\end{enumerate}
	We note $\ordinals$ as the class of all ordinals.
\end{defn}

\begin{prop}[Ordinals are well-ordered]
	Let $a \in \ordinals$ be an ordinal. Then $(a, \in)$ is a well-ordered set.
\end{prop}

\begin{prop}[Ordinality of a well-ordered set]
	For every \marginleft{$\langle A \rangle$} well-ordered set $A$ there is a unique $\langle A \rangle \in \cardinals$ such that $a \ordeq A$. We say $\langle A \rangle$ is the \textbf{ordinality of $A$}. The natural numbers are the initial segment of the ordinals. $\omega$ is the ordinal associated with the natural numbers.
\end{prop}

\begin{remark}
	As an example, consider the von Neumann ordinal $3 = (0, 1, 2)$ as a well-ordered set. We can see it as a sequence of three element, which means the last is the third. Similarly, the ordinality of the set $(a_1, a_2, a_3)$ is $3 = (0, 1, 2)$ as they define well-ordered set with the same ordering. The definitions are such that these ideas extend to infinite sets.
\end{remark}

\begin{defn}[Ordinal addition]
	Let $(A, \leq_A)$ \marginleft{Ordinal addition: $\langle A \rangle + \langle B \rangle$} and $(B, \leq_B)$ be two well ordered sets. Let $(A \sqcup B, \leq)$ be the POS where:
	\begin{itemize}
		\item $(A, a_1) \leq (A, a_2)$ if $a_1 \leq_A a_2$
		\item $(B, b_2) \leq (B, b_2)$ if $b_1 \leq_B b_2$
		\item $(A, a) \leq (B, b)$ for all $a \in A$ and $b \in B$.  	
	\end{itemize}
	Then $(A \sqcup B, \leq)$ is well-ordered and the ordinal $\langle A \sqcup B \rangle$ is fully determined by $\langle A \rangle$ and $\langle B \rangle$. Therefore we can define the \textbf{ordinal addition} $\langle A \rangle + \langle B \rangle =  \langle A \sqcup B \rangle$.
\end{defn}

%\begin{prop}[Ordinal multiplication]The addition has the following properties:
%	\begin{enumerate}
%		\item associative: $\langle A \rangle + ( \langle B \rangle + \langle C \rangle) = (\langle A \rangle + \langle B \rangle) + \langle C \rangle$
%		\item $\langle 0 \rangle = \langle \emptyset \rangle$ is the identity: $\langle A \rangle + \langle 0 \rangle = \langle 0 \rangle + \langle A \rangle = \langle A \rangle$
%		\item not commutative in general: $\langle A \rangle + \langle B \rangle$ not necessarily the same as $\langle B \rangle + \langle A \rangle$
%		\item reduces to arithmetic addition on the natural numbers
%	\end{enumerate}
%\end{prop}

\begin{remark}
	Addition in non-commutative (i.e. $\langle A \rangle + \langle B \rangle \neq \langle B \rangle + \langle A \rangle$) for infinite ordinals. For example $(a_1, a_2, ..., a_n, ...) \sqcup (b_1, b_2, b_3) = (a_1, a_2, ..., a_n, ..., b_1, b_2, b_3)$ is not the same as $(b_1, b_2, b_3) \sqcup (a_1, a_2, ..., a_n, ...) = (b_1, b_2, b_3, a_1, a_2, ..., a_n, ...) \simeq (c_1, c_2, ..., c_n, ...)$. Therefore $\omega + 3 \neq 3 + \omega = \omega$.
\end{remark}

\begin{defn}[Ordinal multiplication]
	Let $(A, \leq_A)$ \marginleft{Ordinal multiplication: $\langle A \rangle \langle B \rangle$} and $(B, \leq_B)$ be two well ordered sets. Let $(A \times B, \leq)$ be the POS where:
	\begin{itemize}
		\item $(a_1, b_1) \leq (a_2, b_2)$ if $b_1 \leq_B b_2$
		\item $(a_1, b) \leq (a_2, b)$ if $a_1 \leq_A a_2$
	\end{itemize}
	Then $(A \times B, \leq)$ is well-ordered and the ordinal $\langle A \times B \rangle$ is fully determined by $\langle A \rangle$ and $\langle B \rangle$. Therefore we can define the \textbf{ordinal multiplication} $\langle A \rangle \langle B \rangle =  \langle A \times B \rangle$.
\end{defn}

%\begin{prop}[Ordinal multiplication]
%	The multiplication has the following properties:
%	\begin{enumerate}
%		\item associative: $\langle A \rangle ( \langle B \rangle \langle C \rangle) = (\langle A \rangle \langle B \rangle) \langle C \rangle$
%		\item $\langle 1 \rangle = \langle \{ \emptyset \} \rangle$ is the identity: $\langle A \rangle \langle 1 \rangle  = \langle 1 \rangle \langle A \rangle = \langle A \rangle$
%		\item right distributive over addition: $\langle A \rangle ( \langle B \rangle + \langle C \rangle) = \langle A \rangle \langle B \rangle + \langle A \rangle \langle C \rangle$
%		\item $\langle A \rangle \langle 0 \rangle  = \langle 0 \rangle \langle A \rangle = \langle 0 \rangle$
%		\item not commutative in general: $\langle A \rangle + \langle B \rangle$ not necessarily the same as $\langle B \rangle + \langle A \rangle$
%		\item reduces to arithmetic multiplication on the natural numbers
%	\end{enumerate}
% The multiplication is associative and $\langle \emptyset \rangle$ is the identity (i.e. $\langle A \rangle + \langle \emptyset \rangle = \langle \emptyset \rangle + \langle A \rangle = \langle A \rangle$). The additions is not, in general, commutative.
%\end{prop}

\begin{remark}
	Muliplication is non-commutative (i.e. $\langle A \rangle \langle B \rangle \neq \langle B \rangle \langle A \rangle$) for infinite ordinals. For example $(a_1, a_2, ..., a_n, ...) \times (b_1, b_2) = ((a_1, b_1), (a_2, b_1), ..., (a_n, b_1), ..., \\ (a_1, b_2), (a_2, b_2), ..., (a_n, b_2), ...)$ is not the same as $(b_1, b_2) \times (a_1, a_2, ..., a_n, ...) = ((b_1, a_1), (b_2, a_1), (b_1, a_2), (b_2, a_2), ..., (b_1, a_n), (b_2, a_n), ...) \simeq (c_1, c_2, ..., c_n, ...)$. \\ Therefore $\omega 2 \neq 2 \omega = \omega$.

	With addition and multiplication, we can get a sense of how the ordinals work. $\omega$ represents a countable sequence. $\omega +3$ is a countable sequence followed by three elements. $\omega + \omega  = \omega2$ represents a countable sequence followed by a countable sequence. $\omega6$ represents a sequence of 6 countable sequences. $\omega\omega = \omega^2$ represents a countable sequence of countable sequences. $\omega^3$ represents a countable sequence of countable sequences of countable sequences. $\omega^\omega$ extends the recursion infinitely many times and so on. There is no upper limit to the ordinals.
\end{remark}

\begin{remark}
	The cardinality of a set (i.e. how many elements it contains) is defined in terms of injection/bijection: a set is smaller than another if it can be injected into it, and it is as big as another if it can be put into a one-to-one correspondence.
\end{remark}

\begin{defn}[Cardinal comparison]
	Let $A$ \marginleft{Cardinality} and $B$ be two sets. If there exists a injective function $f : A \to B$ then we say $A$ \textbf{has lower cardinality than} $B$, noted $A \crdleq B$. If there exists a bijective function we say they have \textbf{the same cardinality}, noted $A \crdeq B$.
\end{defn}

\begin{prop}[Cardinal comparability of sets]
	Given two sets $A$ and $B$, either $A \crdleq B$ or $B \crdleq A$ one must have lower cardinality than the other (i.e. there exists an injective function from one two the other). Additionally, $A \crdeq B$ if and only if $A \crdleq B$ and $B \crdleq A$ (i.e. there exists a bijective function between $A$ and $B$ only if there exists an injective function in both direction).
\end{prop}

\begin{prop}[Well-ordering theorem]
	Every set can be well-ordered.
\end{prop}

\begin{remark}
	The well-ordering theorem allows us to reuse ordinal numbers to quantify cardinality. As two different well-ordered sets may have the same cardinality, we'll take the lowest ordinal between them.
\end{remark}

\begin{defn}[Cardinal number]
	A \textbf{cardinal}  \marginleft{Cardinals: $\cardinals$} is an ordinal $a \in \ordinals$ that has lower ordinality of any ordinal that has the same cardinality. That is, $a \ordleq b$ for all $b \in \ordinals$ such that $a \crdeq b$. The set of all cardinals is noted $\cardinals \subset \ordinals$.
\end{defn}

\begin{prop}[Cardinality of a set]
	For every \marginleft{$|A|$} set $A$ there is a unique $|A| \in \cardinals$ such that $a \crdeq A$. We say $|A|$ is the \textbf{cardinality of $A$}.
\end{prop}

\begin{remark}
\end{remark}

@@

\subsection{Classes, sets and elements}

As some collections cannot \marginright{TODO: diagram with Classes, proper classes and sets.} be put into other collections without creating paradoxes, the resolution of syntactic paradoxes is through the distinction between classes and sets. Classes are all those objects that can contain elements. Sets are particular classes that can also be elements of other classes. Therefore we can have the class of all sets, but we cannot have the set of all sets or the class of all classes.

\subsection{Axiomatization}

There are different approaches to the axiomatization of set theory with different degree of variation. One strategy, refered to as Zermelo–Fraenkel (ZFC), only defines sets. It avoids paradoxes by restricting set construction to subsets only.

Another strategy, refered to as von Neumann–Bernays–Gödel (NBG), starts by defining classes and then defines sets as those classes that can be elements of classes. It avoids paradoxes by restricting set construction on predicates over elements. Since a proper class is not an element, if the definition creates a contradiction for an item $x$ (i.e. we have both $x \in S$ and $x \notin S$) than it must be that the element $x$ is a proper class.

\textbf{Axioms}. Here are the axioms of a particular formulation of axiomatic set theory taken from CITE:
\begin{enumerate}
	\item Axiom of extent. If two classes have the same elements, then they are identical.
	\item Axiom of class construction. Let $P(x)$ be a predicate expressed in terms of the symbols $\in, \OR, \AND, \NOT, \Rightarrow, \exists, \forall$, brackets, variables $x, y, z, A, B, ...$ Then there exists a class $C$ that consists of all the elements x which satisfy $P(x)$.
	\item Every subclass of a set is a set.
	\item $\emptyset$ is a set.
	\item If $a$ and $b$ are sets, then $\{a, b\}$ is a set.
	\item If $\mathcal{A}$ is a set of sets, then, $\bigcup\limits_{A \in \mathcal{A}} A$ is a set.
	\item If $A$ is a set, the power set $\mathcal{P}(A)$ is a set.
	\item Axiom of foundation. If $A \neq \emptyset$ is a set, there exists an element $a \in A$ such that $a \cap A = \emptyset$.
	\item Axiom of replacement. If $A$ is a set and $f : A \to B$ is a surjective function, then $B$ is a set.
	\item Axiom of choice. Every set has a choice function. That is, given a set $A$, there exists a function $f : \mathcal{P}(A) \setminus \{ \emptyset \} \to A$ such that $f(B) \in B$.
	\item Axiom of infinity. There exists a successor set (as defined in \ref{defn_successor_set}).
\end{enumerate}

Cardinal numbers

\begin{prop}[Well-ordering theorem]
	Every set can be well-ordered.
\end{prop}

Define ordering by existence of injection.

def equipotent set (bijective)

prop no surjective funtion from a to P(A)

talk about contiunuum hypo as example of work in set theory

\begin{remark}
	Axiom 1 serves to define class equality. Axiom 2 defines how to define classes based on predicates. Axioms 3-7 tells us that some classes, constructable by axiom 2, are sets. Axiom 8 guarantees that we cannot have an infinite sequences $\{ A_i \}_{i=1}^\infty$ such that $A_{i+1} \in A_i$. In particular, a set cannot be an element of itself. Axiom 9 tells us that any set that is ``smaller'' than a set (i.e. we can map another set onto it) is a set. Axiom 10 guarantees that we can always pick an element from a set, though it does not tell us how. Axiom 11 tells us that there are sets with infinite elements.
\end{remark}
